MultiDataGrowthAssessPico

### 2023-12-08 Code/MultiDataGrowthAssessPico.Rmd
Removed all redundant varibles

library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(photobiologyWavebands)
library(tidyverse)

@@

MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),
                   w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

@@

## List previously processed data

Note: Split files will not be correct for Par_ue, but Actinic_par should be OK Fix: replace MetaData Par_ue with max(Actinic_par) for each file or split file

@@

# TestData <- readRDS_plus(Flnm = file.path("../ProcessedData/LogGrowthFits/20200731_PICO_MCMIX004_RUN17_ProcessDataNestGrowth.Rds"))

@@

@@

# OD720 gompertz fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
lognormOD720_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, lognormOD720_Gompertz_tidied, lognormOD720_Gompertz_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
  unnest(cols = c(lognormOD720_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error, lognormOD720_Gompertz_tidied_statistic, lognormOD720_Gompertz_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
         OD720_Gmu_raw = lognormOD720_Gompertz_tidied_estimate_Gmu,
         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,             
         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag)  %>%
   mutate(OD720_Gmu_corr = if_else(!is.na(OD720_Gmu_raw), OD720_Gmu_raw, 0),
          OD720_Gmu_se = if_else(!is.na(OD720_Gmu_se), OD720_Gmu_se, 0),
          OD720_GLag = if_else(!is.na(OD720_GLag), OD720_GLag, 0),
          OD720_GLag_se = if_else(!is.na(OD720_GLag_se), OD720_GLag_se, 0),
          OD720_Gmax = if_else(!is.na(OD720_Gmax), OD720_Gmax, 0),
          OD720_Gmax_se = if_else(!is.na(OD720_Gmax_se), OD720_Gmax_se, 0),
          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720_Gmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720_Gmu_corr >= 0, OD720_Gmu_corr, 0),
          # OD720_GseGrowthFlag = case_when(OD720_Gmu_corr > 0 & OD720_Gmu_corr * GrowthFlagError > OD720_Gmu_se ~ 1,
          #                                   OD720_Gmu_corr > 0 & OD720_Gmu_corr * GrowthFlagError < OD720_Gmu_se ~ 0,
          #                                   OD720_Gmu_corr == 0 ~ 1),

           OD720_GseGrowthFlag = if_else(OD720_Gmu_se < OD720_Gmu_corr * GrowthFlagError, 1, 0),
   )

# deltaOD gompertz fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
lognormdeltaOD_unnest <- LogFitsData %>% 
select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, lognormdeltaOD_Gompertz_tidied, lognormdeltaOD_Gompertz_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
       ) %>%
unnest(cols = c(lognormdeltaOD_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error, lognormdeltaOD_Gompertz_tidied_statistic, lognormdeltaOD_Gompertz_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
         deltaOD_Gmu_raw = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
   mutate(deltaOD_Gmu_corr = if_else(!is.na(deltaOD_Gmu_raw), deltaOD_Gmu_raw, 0),
          deltaOD_Gmu_se = if_else(!is.na(deltaOD_Gmu_se), deltaOD_Gmu_se, 0),
          deltaOD_GLag = if_else(!is.na(deltaOD_GLag), deltaOD_GLag, 0),
          deltaOD_GLag_se = if_else(!is.na(deltaOD_GLag_se), deltaOD_GLag_se, 0),
          deltaOD_Gmax = if_else(!is.na(deltaOD_Gmax), deltaOD_Gmax, 0),
          deltaOD_Gmax_se = if_else(!is.na(deltaOD_Gmax_se), deltaOD_Gmax_se, 0),
          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaOD_Gmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaOD_Gmu_corr >= 0, deltaOD_Gmu_corr, 0),
          # deltaOD_GseGrowthFlag = case_when(deltaOD_Gmu_corr > 0 & deltaOD_Gmu_corr * GrowthFlagError > deltaOD_Gmu_se ~ 1,
          #                                   deltaOD_Gmu_corr > 0 & deltaOD_Gmu_corr * GrowthFlagError < deltaOD_Gmu_se ~ 0,
          #                                   deltaOD_Gmu_corr == 0 ~ 1),

         deltaOD_GseGrowthFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu_corr * GrowthFlagError, 1, 0),
          )

# OD720 logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
OD720_unnest <- LogFitsData %>%
  select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720_logistic_tidied, OD720_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
         ) %>%
  unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu_raw = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,             
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
   mutate(OD720_Lmu_corr = if_else(!is.na(OD720_Lmu_raw), OD720_Lmu_raw, 0),
          OD720_Lmu_se = if_else(!is.na(OD720_Lmu_se), OD720_Lmu_se, 0),
          OD720_Lintercept = if_else(!is.na(OD720_Lintercept), OD720_Lintercept, 0),
          OD720_Lintercept_se = if_else(!is.na(OD720_Lintercept_se), OD720_Lintercept_se, 0),
          OD720_Lmax = if_else(!is.na(OD720_Lmax), OD720_Lmax, 0),
          OD720_Lmax_se = if_else(!is.na(OD720_Lmax_se), OD720_Lmax_se, 0),
          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720_Lmu_corr >= 0 , OD720_Lmu_corr, 0),
          # OD720_LseGrowthFlag = case_when(OD720_Lmu_corr > 0 & OD720_Lmu_corr * GrowthFlagError > OD720_Lmu_se ~ 1,
          #                                   OD720_Lmu_corr > 0 & OD720_Lmu_corr * GrowthFlagError < OD720_Lmu_se ~ 0,
          #                                   OD720_Lmu_corr == 0 ~ 1),
          OD720_LseGrowthFlag = if_else(OD720_Lmu_se < OD720_Lmu_corr * GrowthFlagError, 1, 0),
          OD720_TimeHalfPmax_h = (log(2-(OD720_Lintercept/(OD720_Lmax - OD720_Lintercept))))/OD720_Lmu_corr,
          OD720_TimeHalfPmax_h = if_else(!is.infinite(OD720_TimeHalfPmax_h), OD720_TimeHalfPmax_h, 0),
          OD720_TimeHalfPmax_h = if_else(!is.nan(OD720_TimeHalfPmax_h), OD720_TimeHalfPmax_h, 0)
          )

# deltaOD logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007 and less than 14 days.Defined at line 75 
deltaOD_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720,  GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, deltaOD_logistic_tidied, deltaOD_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu_raw = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
   mutate(deltaOD_Lmu_corr = if_else(!is.na(deltaOD_Lmu_raw), deltaOD_Lmu_raw, 0),
          deltaOD_Lmu_se = if_else(!is.na(deltaOD_Lmu_se), deltaOD_Lmu_se, 0),
          deltaOD_Lintercept = if_else(!is.na(deltaOD_Lintercept), deltaOD_Lintercept, 0),
          deltaOD_Lintercept_se = if_else(!is.na(deltaOD_Lintercept_se), deltaOD_Lintercept_se, 0),
          deltaOD_Lmax = if_else(!is.na(deltaOD_Lmax), deltaOD_Lmax, 0),
          deltaOD_Lmax_se = if_else(!is.na(deltaOD_Lmax_se), deltaOD_Lmax_se, 0),
          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaOD_Lmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaOD_Lmu_corr >= 0, deltaOD_Lmu_corr, 0),
          # deltaOD_LseGrowthFlag = case_when(deltaOD_Lmu_corr > 0 & deltaOD_Lmu_corr * GrowthFlagError > deltaOD_Lmu_se ~ 1,
                                            # deltaOD_Lmu_corr > 0 & deltaOD_Lmu_corr * GrowthFlagError < deltaOD_Lmu_se ~ 0,
                                            # deltaOD_Lmu_corr == 0 ~ 1),
         deltaOD_LseGrowthFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu_corr * GrowthFlagError, 1, 0),
          deltaOD_TimeHalfPmax_h = (log(2-(deltaOD_Lintercept/(deltaOD_Lmax - deltaOD_Lintercept))))/deltaOD_Lmu_corr,
          deltaOD_TimeHalfPmax_h = if_else(!is.infinite(deltaOD_TimeHalfPmax_h), deltaOD_TimeHalfPmax_h, 0),
          deltaOD_TimeHalfPmax_h = if_else(!is.nan(deltaOD_TimeHalfPmax_h), deltaOD_TimeHalfPmax_h, 0)
          )

# OD720 truncated logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
OD720truncLog_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720trunc_logistic_tidied, OD720trunc_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
  unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
         OD720trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
         OD720trunc_Lmu_raw = OD720trunc_logistic_tidied_estimate_Lmu,
         OD720trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu,
         OD720trunc_Lintercept = OD720trunc_logistic_tidied_estimate_Lintercept,             
         OD720trunc_Lintercept_se = OD720trunc_logistic_tidied_std.error_Lintercept)  %>%
   mutate(OD720trunc_Lmu_corr = if_else(!is.na(OD720trunc_Lmu_raw), OD720trunc_Lmu_raw, 0),
          OD720trunc_Lmu_se = if_else(!is.na(OD720trunc_Lmu_se), OD720trunc_Lmu_se, 0),
          OD720trunc_Lintercept = if_else(!is.na(OD720trunc_Lintercept), OD720trunc_Lintercept, 0),
          OD720trunc_Lintercept_se = if_else(!is.na(OD720trunc_Lintercept_se), OD720trunc_Lintercept_se, 0),
          OD720trunc_Lmax = if_else(!is.na(OD720trunc_Lmax), OD720trunc_Lmax, 0),
          OD720trunc_Lmax_se = if_else(!is.na(OD720trunc_Lmax_se), OD720trunc_Lmax_se, 0),
          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720trunc_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720trunc_Lmu_corr >= 0 , OD720trunc_Lmu_corr, 0),
          # OD720trunc_LseGrowthFlag = case_when(OD720trunc_Lmu_corr > 0 & OD720trunc_Lmu_corr * GrowthFlagError > OD720trunc_Lmu_se ~ 1,
          #                                   OD720trunc_Lmu_corr > 0 & OD720trunc_Lmu_corr * GrowthFlagError < OD720trunc_Lmu_se ~ 0,
          #                                   OD720trunc_Lmu_corr == 0 ~ 1),

           OD720trunc_LseGrowthFlag = if_else(OD720trunc_Lmu_se < OD720trunc_Lmu_corr * GrowthFlagError, 1, 0),
          OD720trunc_TimeHalfPmax_h = (log(2-(OD720trunc_Lintercept/(OD720trunc_Lmax - OD720trunc_Lintercept))))/OD720trunc_Lmu_corr,
          OD720trunc_TimeHalfPmax_h = if_else(!is.infinite(OD720trunc_TimeHalfPmax_h), OD720trunc_TimeHalfPmax_h, 0),
          OD720trunc_TimeHalfPmax_h = if_else(!is.nan(OD720trunc_TimeHalfPmax_h), OD720trunc_TimeHalfPmax_h, 0)
          )

>>>>

library(lubridate)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(photobiologyWavebands)
library(tidyverse)

@@

MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(450), w_length2rgb(470), w_length2rgb(530),
                   w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

@@

## List processed data

@@

@@

glimpse(LogFitsData)

@@

# OD720 logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.

OD720_unnest <- LogFitsData %>%
  select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Optode, OptodeCh, OptodeMeasure, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD,  GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, OD720_logistic_tidied, OD720_logistic_predict, O2_Category)
         ) %>%
  unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu_raw = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,             
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
   mutate(OD720_Lmu_corr = if_else(!is.na(OD720_Lmu_raw), OD720_Lmu_raw, 0),
          OD720_Lmu_se = if_else(!is.na(OD720_Lmu_se), OD720_Lmu_se, 0),
          OD720_Lintercept = if_else(!is.na(OD720_Lintercept), OD720_Lintercept, 0),
          OD720_Lintercept_se = if_else(!is.na(OD720_Lintercept_se), OD720_Lintercept_se, 0),
          OD720_Lmax = if_else(!is.na(OD720_Lmax), OD720_Lmax, 0),
          OD720_Lmax_se = if_else(!is.na(OD720_Lmax_se), OD720_Lmax_se, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720_Lmu_corr >= 0 , OD720_Lmu_corr, 0),
          OD720_LseGrowthFlag = if_else(OD720_Lmu_se < OD720_Lmu_corr * GrowthFlagError, 1, 0)
          )

# deltaOD logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.

deltaOD_unnest <- LogFitsData %>%
   select(c(Filename,  Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaOD_logistic_tidied, deltaOD_logistic_predict, O2_Category)
          ) %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu_raw = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
   mutate(deltaOD_Lmu_corr = if_else(!is.na(deltaOD_Lmu_raw), deltaOD_Lmu_raw, 0),
          deltaOD_Lmu_se = if_else(!is.na(deltaOD_Lmu_se), deltaOD_Lmu_se, 0),
          deltaOD_Lintercept = if_else(!is.na(deltaOD_Lintercept), deltaOD_Lintercept, 0),
          deltaOD_Lintercept_se = if_else(!is.na(deltaOD_Lintercept_se), deltaOD_Lintercept_se, 0),
          deltaOD_Lmax = if_else(!is.na(deltaOD_Lmax), deltaOD_Lmax, 0),
          deltaOD_Lmax_se = if_else(!is.na(deltaOD_Lmax_se), deltaOD_Lmax_se, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaOD_Lmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaOD_Lmu_corr >= 0, deltaOD_Lmu_corr, 0),
         deltaOD_LseGrowthFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu_corr * GrowthFlagError, 1, 0)
          )

# OD720 truncated logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.

OD720truncLog_unnest <- LogFitsData %>%
   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days,OD720trunc_logistic_tidied, OD720trunc_logistic_predict, O2_Category)
          ) %>%
  unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
         OD720trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
         OD720trunc_Lmu_raw = OD720trunc_logistic_tidied_estimate_Lmu,
         OD720trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu,
         OD720trunc_Lintercept = OD720trunc_logistic_tidied_estimate_Lintercept,             
         OD720trunc_Lintercept_se = OD720trunc_logistic_tidied_std.error_Lintercept)  %>%
   mutate(OD720trunc_Lmu_corr = if_else(!is.na(OD720trunc_Lmu_raw), OD720trunc_Lmu_raw, 0),
          OD720trunc_Lmu_se = if_else(!is.na(OD720trunc_Lmu_se), OD720trunc_Lmu_se, 0),
          OD720trunc_Lintercept = if_else(!is.na(OD720trunc_Lintercept), OD720trunc_Lintercept, 0),
          OD720trunc_Lintercept_se = if_else(!is.na(OD720trunc_Lintercept_se), OD720trunc_Lintercept_se, 0),
          OD720trunc_Lmax = if_else(!is.na(OD720trunc_Lmax), OD720trunc_Lmax, 0),
          OD720trunc_Lmax_se = if_else(!is.na(OD720trunc_Lmax_se), OD720trunc_Lmax_se, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720trunc_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720trunc_Lmu_corr >= 0 , OD720trunc_Lmu_corr, 0),
          OD720trunc_LseGrowthFlag = if_else(OD720trunc_Lmu_se < OD720trunc_Lmu_corr * GrowthFlagError, 1, 0)
          )

# deltaOD truncated logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.

deltaODtruncLog_unnest <- LogFitsData %>%
   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaODtrunc_logistic_tidied, deltaODtrunc_logistic_predict, O2_Category)
          ) %>%
unnest(cols = c(deltaODtrunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaODtrunc_logistic_tidied_term, values_from = c(deltaODtrunc_logistic_tidied_estimate, deltaODtrunc_logistic_tidied_std.error, deltaODtrunc_logistic_tidied_statistic, deltaODtrunc_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaODtrunc_Lmax = deltaODtrunc_logistic_tidied_estimate_Lmax,
         deltaODtrunc_Lmax_se = deltaODtrunc_logistic_tidied_std.error_Lmax,
         deltaODtrunc_Lmu_raw = deltaODtrunc_logistic_tidied_estimate_Lmu,
         deltaODtrunc_Lmu_se = deltaODtrunc_logistic_tidied_std.error_Lmu,
         deltaODtrunc_Lintercept = deltaODtrunc_logistic_tidied_estimate_Lintercept,
         deltaODtrunc_Lintercept_se = deltaODtrunc_logistic_tidied_std.error_Lintercept) %>%
   mutate(deltaODtrunc_Lmu_corr = if_else(!is.na(deltaODtrunc_Lmu_raw), deltaODtrunc_Lmu_raw, 0),
          deltaODtrunc_Lmu_se = if_else(!is.na(deltaODtrunc_Lmu_se), deltaODtrunc_Lmu_se, 0),
          deltaODtrunc_Lintercept = if_else(!is.na(deltaODtrunc_Lintercept), deltaODtrunc_Lintercept, 0),
          deltaODtrunc_Lintercept_se = if_else(!is.na(deltaODtrunc_Lintercept_se), deltaODtrunc_Lintercept_se, 0),
          deltaODtrunc_Lmax = if_else(!is.na(deltaODtrunc_Lmax), deltaODtrunc_Lmax, 0),
          deltaODtrunc_Lmax_se = if_else(!is.na(deltaODtrunc_Lmax_se), deltaODtrunc_Lmax_se, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaODtrunc_Lmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaODtrunc_Lmu_corr >= 0, deltaODtrunc_Lmu_corr, 0),
          deltaODtrunc_LseGrowthFlag = if_else(deltaODtrunc_Lmu_se < deltaODtrunc_Lmu_corr * GrowthFlagError, 1, 0)
          )
